Measuring Bibliometric Coverage of German Law Journals

### 2025-04-24 docs/paper.qmd
Fix wrong fig. 3

>>>>

sets = {
    'KJB': '../data/web_lists/karlsruher-juristische-bibliographie-2024-12-13.csv',
    'juris (2002)': '../data/web_lists/juris-ingested-journals-2002.csv',
    'Wikipedia': '../data/wikipedia/category-law-journal-germany-with-issn.csv'
}
abbrevs = {}
for set_name, file_path in sets.items():
    df = pd.read_csv(file_path)
    abbreviations = df['abbreviation'].dropna().str.lower().tolist()
    abbrevs[set_name] = set(segment.lower().strip() for abbrev in abbreviations for segment in abbrev.split(',') if segment.strip())
